Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-20 WSSSPE2_report/WSSSPE2_review.tex
Section 4: Dan's summary : Format and removed one word "currently".

\item \textbf{Daniel S. Katz: Implementing Transitive Credit with JSON-LD.}
Science and engineering research increasingly relies on activities that facilitate research but are not currently rewarded or recognized, such as: data sharing; developing common data resources, software and methodologies; and annotating data and publications. To promote and advance these activities, we must develop mechanisms for assigning credit, facilitate the appropriate attribution of research outcomes, devise incentives for activities that facilitate research, and allocate funds to maximize return on investment. Katz discussed the issue of assigning credit for both direct and indirect contributions by using JSON-LD to implement a prototype transitive credit system~\cite{Katz_transitive_credit_poster}.

>>>>

\item \textbf{Daniel S. Katz: Implementing Transitive Credit with JSON-LD.}
Science and engineering research increasingly relies on activities that
facilitate research but are not rewarded or recognized, such as: data
sharing; developing common data resources, software and methodologies; and
annotating data and publications. To promote and advance these activities, we
must develop mechanisms for assigning credit, facilitate the appropriate
attribution of research outcomes, devise incentives for activities that
facilitate research, and allocate funds to maximize return on investment. Katz
discussed the issue of assigning credit for both direct and indirect
contributions by using JSON-LD to implement a prototype transitive credit
system~\cite{Katz_transitive_credit_poster}.
